Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Added @deantares tables to the paper for issue #37. @unintendedbear or @amorag just three cells to fill, please finish the table and close the issue :)

\documentclass[preprint]{elsarticle}
\biboptions{round, numbers}
\usepackage[latin1]{inputenc}
%\usepackage[T1]{fontenc}
%\usepackage{textcomp}
\usepackage{array,booktabs,graphicx}
\usepackage{color}
%\usepackage{setspace}
\usepackage{url}
\usepackage[english]{babel}

@@

MUSES is mainly a free, open-source, platform independent solution, and adopts the recommended best practices by Romer \cite{Romer14BestPractices}. %Está bien aquí Fergu?
These features make it a good alternative to most of the proprietary, close and system-specific tools presented in Section \ref{sec:toolsreview} (all but WSO2). In addition, most of the existing tools take into account only smartphones and tablets, but MUSES also covers laptops and company PCs, thus, it is not only for BYOD. Moreover, the companies which might want to work with one of the reviewed systems need a specific operating system in the server, being even more restrictive in some cases. This is specially remarkable in the case of the Blackphone, forcing the companies and the employees to purchase a specific device. MUSES is a good solution towards these cases, since it is a multi-platform system in both the client and the server. 
Table \ref{tab:comparison} summarizes the features of the main analyzed tools, regarding these facts.
% Antonio - Antares, ¿podrías incluir en la comparativa las otras herramientas que se han analizado? Las de Citrix, WSO2, Azzurri, Good...

@@

  \centering
  \renewcommand{\arraystretch}{1.5}% Spread rows out...
%  \resizebox{8cm}{!}{
  \begin{tabular}{>{\centering\bfseries}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering\arraybackslash}m{1in}}
    \toprule
      & \textbf{License} & \textbf{Devices} & \textbf{Price} \\
    \midrule
    MUSES & Free software & IOS, Android, Windows Phone & Free  \\
    IBM Mobile Security & Proprietary &  &  \\
    Sophos Mobile Control & Proprietary & IOS, Android, Windows Phone  &  By Request\\
    Samsung Knox and Blackberry Balance & Proprietary & IOS, Android, Samsung Devices & 12\$ per year/device \\
    Blackphone & Proprietary & Own device & 120\$ per year \\
    Android for Work & Proprietary & Android and devices with Chrome Browser &  12\$ per month/user\\
    \bottomrule
  \end{tabular}
%  }
  \caption{Features of the analyzed products considering licenses, type of devices and price. \label{tab:comparison}}
\end{table}
% Antonio - Antares, ¿no había más tablas?
% Por favor, que alguien rellene los datos de la solución de IBM. ¿Fergu?¿Antares?
% Quizá habría que indicar que MUSES se puede instalar en PC también en la tabla. ¿Sabéis si los demás se puede o son sólo para smartphones/tablets?

>>>>

\documentclass[preprint]{elsarticle}
\biboptions{round, numbers}
\usepackage[latin1]{inputenc}
%\usepackage[T1]{fontenc}
%\usepackage{textcomp}
\usepackage{array,booktabs,graphicx}
\usepackage{color}
%\usepackage{setspace}
\usepackage{url}
\usepackage[english]{babel}
\usepackage{colortbl, pifont}% http://ctan.org/pkg/{array,booktabs}

\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\nmark}{\scalebox{1.25}{\textbf{-}} }

@@

MUSES is mainly a free, open-source, platform independent solution, and adopts the recommended best practices by Romer \cite{Romer14BestPractices}. %Está bien aquí Fergu?
These features make it a good alternative to most of the proprietary, close and system-specific tools presented in Section \ref{sec:toolsreview} (all but WSO2). In addition, most of the existing tools take into account only smartphones and tablets, but MUSES also covers laptops and company PCs, thus, it is not only for BYOD. Moreover, the companies which might want to work with one of the reviewed systems need a specific operating system in the server, being even more restrictive in some cases. This is specially remarkable in the case of the Blackphone, forcing the companies and the employees to purchase a specific device. MUSES is a good solution towards these cases, since it is a multi-platform system in both the client and the server. 
Table \ref{tab:taxonomy} summarizes the features of the main analyzed tools, regarding the proposed taxonomy of Section \ref{sec:toolsreview}. Also, Table \ref{tab:features} shows the features of the analyzed products considering licenses, type of devices and price.
% Antonio - Antares, ¿podrías incluir en la comparativa las otras herramientas que se han analizado? Las de Citrix, WSO2, Azzurri, Good...

@@

  \centering
  \renewcommand{\arraystretch}{1.8}% Spread rows out...
  \resizebox{12cm}{!}{
  \begin{tabular}{>{\centering\bfseries}m{0.8in} >{\centering}m{0.8in} >{\centering}m{0.8in} >{\centering}m{0.8in} >{\centering}m{0.8in} >{\centering\arraybackslash}m{0.8in}}
    \toprule
      & \textbf{Offline threat detection method} & \textbf{Updatable database} & \textbf{Standalone} & \textbf{Non-invasive data access} & \textbf{Superuser system control} \\
    \midrule
    MUSES & \cmark & \cmark & \cmark & \cmark & \cmark  \\
     \arrayrulecolor[gray]{0.8}\hline
    IBM Mobile Security & \xmark & \xmark & \cmark & \xmark & \xmark  \\
     \arrayrulecolor[gray]{0.8}\hline
    Sophos Mobile Control & \cmark & \xmark & \cmark & \xmark & \xmark \\
     \arrayrulecolor[gray]{0.8}\hline
    Samsung Knox & \cmark & \nmark & \cmark & \nmark & \cmark\\
     \arrayrulecolor[gray]{0.8}\hline
     Blackbery Balance & \nmark & \nmark & \cmark & \nmark & \cmark\\
     \arrayrulecolor[gray]{0.8}\hline
    Blackphone & \nmark & \nmark & \cmark & \cmark & \nmark\\
     \arrayrulecolor[gray]{0.8}\hline
    Android for Work & \xmark & \xmark & \cmark & \xmark & \cmark\\
    \bottomrule
  \end{tabular}
  }
  \caption{Proposed taxonomy to classify the BYOD tools described in this paper.}
  \label{tab:taxonomy}
\end{table}

  \centering
  \renewcommand{\arraystretch}{1.8}% Spread rows out...
%  \resizebox{8cm}{!}{
  \begin{tabular}{>{\centering\bfseries}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering\arraybackslash}m{1in}}
       \toprule
      & \textbf{License} & \textbf{Devices} & \textbf{Price} \\
       \midrule
    MUSES & OpenSource &  & Free*  \\
       \arrayrulecolor[gray]{0.8}\hline
    IBM Mobile Security & Proprietary &  &  \\
        \arrayrulecolor[gray]{0.8}\hline
    Sophos Mobile Control & Proprietary & IOS, Android, Windows Phone  &  By Request\\
        \arrayrulecolor[gray]{0.8}\hline
    Samsung Knox and Blackbery Balance & Proprietary & Android Samsung Devices and IOS & 12\$ per year/device \\
        \arrayrulecolor[gray]{0.8}\hline
    Blackphone & Proprietary & Own device & 120\$ per year \\
        \arrayrulecolor[gray]{0.8}\hline
    Android for Work & Proprietary & Android and devices with Chrome Browser &  12\$ per month/user\\
       \bottomrule
  \end{tabular}
%  }
  \caption{Features of the analyzed products considering licenses, type of devices and price.}
  \label{tab:features}
\end{table}
% Antonio - Antares, ¿no había más tablas?
% Por favor, que alguien rellene los datos de la solución de IBM. ¿Fergu?¿Antares?
% Quizá habría que indicar que MUSES se puede instalar en PC también en la tabla. ¿Sabéis si los demás se puede o son sólo para smartphones/tablets?
